---
title: "Targeting Dashboards"
output: html_document
---

```{r, echo = F}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```


```{r, echo=F}
library(tidyverse)
# Sample dataframe with iso2c and country variables
df <- readr::read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTVkw2cJ5IqeOTBKOfBXpDZDftW9g_nlN-ZKdqDK42wvcxZYHbkVBKDsxfB8r7V88RVef3zHIxBbDOw/pub?output=csv") %>% 
  janitor::clean_names() %>%  
  mutate(iso2c = city,
         country = str_to_title(iso2c)) %>% 
      distinct(iso2c, country) %>% 
      drop_na()

# Generate HTML code
html_code <- sprintf('<div id="overlay">
                        <button id="selectButton" style="padding: 10px; border: 1px solid #ccc; border-radius: 5px; font-size: 16px; cursor: pointer;">Select Municipality/Race</button>
                        <select id="iframeSelector" style="display:none; padding: 10px; border: 1px solid #ccc; border-radius: 5px; font-size: 16px; cursor: pointer;">
                          <option value="" disabled selected>Select Municipality/Race</option>
                          %s
                        </select>
                      </div>',
                      paste(sprintf('<option value="%s">%s</option>', df$iso2c, df$country), collapse = "\n"))

# Print the HTML code
shiny::HTML(html_code)

```




<!-- <iframe id="iframeDisplay" style="border:none; position:fixed; top:0; left:0; width:100%; height:100vh;" src='https://favstats.github.io/locturkex2024/artillary.html'></iframe> -->
<iframe id="iframeDisplay" style="border:none; position:fixed; top:0; left:0; width:100%; height:100vh;" src="https://favstats.github.io/locturkex2024/docs/map"></iframe>

<link rel="stylesheet" href="https://cdn.jsdelivr.net/npm/choices.js@9.0.1/public/assets/styles/choices.min.css">
<script src="https://cdn.jsdelivr.net/npm/choices.js@9.0.1/public/assets/scripts/choices.min.js"></script>

<script>
  // Use window.onload to make sure all resources are loaded
  window.onload = function() {
    const selectButton = document.getElementById('selectButton');
    const iframeSelector = document.getElementById('iframeSelector');
    const iframeDisplay = document.getElementById('iframeDisplay');
    
    
    // Set a maximum length for the src attribute
    const maxLength = 100;  // Example length limit

    // Check if the current src length exceeds maxLength and if so, set the default src
    if(iframeDisplay.src.length > maxLength) {
      iframeDisplay.src = 'https://favstats.github.io/locturkex2024/artillary';
    }
    
    if(iframeSelector) {
      // Now we know iframeSelector is present, we can safely initialize Choices
      const choices = new Choices(iframeSelector, {
        searchEnabled: true,
        shouldSort: false,
        itemSelectText: '',
      });
    
      selectButton.addEventListener('click', function() {
        selectButton.style.display = 'none';
        iframeSelector.style.display = 'block';
      });
    
      iframeSelector.addEventListener('change', function() {
        const selectedOption = iframeSelector.value;
        iframeDisplay.src = `https://favstats.github.io/locturkex2024/${selectedOption}`;
        selectButton.textContent = iframeSelector.options[iframeSelector.selectedIndex].text;
        iframeSelector.style.display = 'none';
        selectButton.style.display = 'block';
      });
    } else {
            
      iframeDisplay.src = `artillary.html`;
      console.error("Can't find the iframeSelector element!");
    }
  };
</script>

<style>
#overlay {
  z-index: 1001; /* Ensure the overlay is above everything else */
}
#selectButton {
  padding: 10px; /* Adjust padding as needed */
  border: 1px solid #ccc;
  border-radius: 5px;
  font-size: 16px; /* Adjust font size as needed */
  cursor: pointer;
  position: absolute;
  top: 10px; /* Adjust top as needed */
  right: 30px; /* Adjust right as needed */
  z-index: 1001; /* Make sure the button is above the overlay */
  min-width: 120px; /* Set a fixed minimum width for the button */
  background-color: #f0f0f0; /* Button background color */
  color: #333; /* Button text color */
  transition: background-color 0.3s, color 0.3s; /* Smooth transition */
}

.choices {
  position: fixed;
  top: 10px; /* Adjust top as needed */
  right: 30px; /* Adjust right as needed */
  z-index: 1001; /* Make sure the dropdown is above the overlay */
  min-width: 300px; /* Set a fixed minimum width for the dropdown */
}
</style>





